Machine Learning Methods for Discourse Segmentation of Communications in E-Mail Based Behavioral Interventions

### 2018-08-04 paper-amia-summit-2018/manuscript.tex
Fixed all issues reviewed by Alex on the first draft

In this paper, results are reported by ``new segment'' class as well as weighted average over both classes to avoid confusion regarding overall model performance due to severe class imbalance. In addition, standard metrics: precision, recall and F1-measure were used to eliminate doubt about the model performance since accuracy is misleading for imbalanced datasets. AUC is also utilized due to its effectiveness in measuring the quality of binary classifiers for imbalanced datasets,\cite{hu2015kernelized} which are demonstrated by the ROC curves in Figure~\ref{fig:roc-curves}.

>>>>

In this paper, results are reported by ``new segment'' class as well as weighted average over both classes to avoid confusion regarding overall model performance due to severe class imbalance. In addition, standard metrics: precision, recall and F1-measure were used to eliminate doubt about the model performance since accuracy is misleading for imbalanced datasets. AUC is also utilized due to its effectiveness in measuring the quality of binary classifiers for imbalanced datasets,\cite{hu2015kernelized} which are also demonstrated by the ROC curves in Figure~\ref{fig:roc-curves}.
